---
title: "HW 06 - Legos"
author: "Raya Shelashska,"
date: "July 19, 2022"
output: github_document
editor_options: 
  chunk_output_type: console
---

## Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse)
library(dsbox)
```

## Exercises

### Exercise 1

Three the most common names of purchasers are Jackson, Jacob, and Joseph.
```{r top-3-names}
lego_sales %>%
  count(first_name, sort = TRUE) %>%
  top_n(3)
```

### Exercise 2

Three the most common themes of Lego sets: Star Wars, Nexo Knights, and Gear.
```{r top-3-themes}
lego_sales %>%
  count(theme, sort = TRUE) %>%
  top_n(3)
```


### Exercise 3

```{r top-3-subthemes-1}
lego_sales %>%
  filter(theme == "Star Wars") %>%
  count(subtheme, sort = TRUE) %>%
  top_n(3)
# is there is a way to make it one chunk? I tried to add more themes in the filter line but it didn't work
```

```{r top-3-subthemes-2}
lego_sales %>%
  filter(theme == "SNexo Knights") %>%
  count(subtheme, sort = TRUE) %>%
  top_n(3)
```

```{r top-3-subthemes-3}
lego_sales %>%
  filter(theme == "Gear") %>%
  count(subtheme, sort = TRUE) %>%
  top_n(3)
```

### Exercise 4

```{r age_grouping}
lego_sales <- lego_sales %>%
  mutate(age_group = case_when(
    age <= 18 ~ "18 and under",
    age > 18 & age <= 25 ~ "19 - 25",
    age > 25 & age <= 35 ~ "26 - 35",
    age > 35 & age <= 50 ~ "36 - 50", 
    age > 50 ~ "51 and over"
    ))

```


### Exercise 5

36-50 years-old-group made the most purchases 
```{r age-purchase}
lego_sales %>%
  group_by(age_group) %>%
  summarise(total_n = sum(quantity)) %>%
  arrange(desc(total_n))
```


### Exercise 6
36-50-years-old group spent the most money - $6642
```{r age-money-spent}
lego_sales %>%
  group_by(age_group) %>%
  summarise(total_n = sum(us_price)) %>%
  arrange(desc(total_n))
```


### Exercise 7

Star Wars made the most profit for Lego
```{r lego-theme-profit}
lego_sales %>%
  group_by(theme) %>%
  summarise(total_n = sum(us_price)) %>%
  arrange(desc(total_n))
```


### Exercise 8

```{r area-code}
#I don't know how to wrap my mind around it. I can't figure it out. Sorry. 
```


### Exercise 9

Question: How big Lego sets do different age groups purchase? Customers 36-50 years old tend to buy bigger Lego sets than other age groups. The age 18 and under tend to buy smaller Lego sets than other age groups. 
```{r visualization}

ggplot(data = lego_sales, aes(x = age_group, y =  pieces)) +
  geom_boxplot() +
  labs(
    title = "Size of Lego sets purchased based on the age group",
    x = "Age group", y = "Number of pieces in lego set") +
  theme_minimal()
 
```


```{r}
ggplot(data = lego_sales, aes(x = age_group, color = pieces, fill = pieces)) +
  geom_bar()
#why there is no color? What did I miss?
```



